---
title: "Prediction using Supervised ML"
author: "Aditya Dawn"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### **Objective of the Task**  
  
This was a task with Simple Linear Regression Equation. Here, we were asked to predict the score of a student if he studies for 9.25 hours per day.
  
  
  
##### *Tools used*  
  
* R for building the linear model.
* R Markdown for making this presentation.
  
  
  
#### **What is Simple Linear Regression?**  

Simple Linear Regression is a technique to find the association between two variables (a dependent variable and an independent variable). It is a kind of Supervised Learning function to build a model and predict the value of the dependent variable based on new value of the independent variable.  
  
  
  
#### **Mathematical Relation**  
  
The mathematical equation can be generalised as follows :
$$y = \beta_0 + \beta_1*x$$  
where,  
"y" is the dependent variable  
"x" is the independent variable  
"$\beta_0$ is the Intercept  
"$\beta_1$" is the Regression Coefficient  
  *Intercept is the value of the dependent variable when the value of the independent variable is 0.*  
  *Regression Coefficient is the effect of independent variable on the estimation of dependent variable's value.*  
  Here, we have to estimate the values of $\beta_0$ and $\beta_1$.  
    
    
    
#### **Importing Data**  

Let us import the data from the given link in the task slide.
```{r echo=TRUE}
df <- read.csv(url("http://bit.ly/w-data"))
```



#### **Structure of the data** 
```{r echo=TRUE}
str(df)
dim(df)
```
Clearly, the data has 2 features with 25 observations in each of them.  


#### **Nature of the given Data**
```{r echo=TRUE}
typeof(df$Hours)
typeof(df$Scores)
```
So, as shown by the output :  

* The feature "Hours" consists of double characters.
* The feature "Scores" consists of integer characters.  



#### **Finding Missing Values (if any)**
```{r echo=TRUE}
summary(df)
```
So, it is clear that, there are no missing observations in the data.  



#### **Visual Representation**
Now, let us look at a visual representation of the data.  
```{r echo=TRUE}
library(ggplot2)
library(ggExtra)
ggMarginal( ggplot( df, aes( x=Hours,y=Scores)) +
            geom_point( color = 'red' ,size = 3) +
            labs ( title = '\nScatter Plot') +
            theme(legend.position="none"), 
            type="boxplot"
           )
```
##### **Observations :-**  
 
 * There are no outliers as shown by the marginal  boxplots of the features.
 * There is a correlation between *Hours* and *Scores* as it is clear from the plot that, with increase in the *Hours* the *Scores* increases  

##### **Correlation Coefficient**  
The above analysis can be verified by calculating the correlation coefficient between *Scores* and *Hours*.
```{r echo=TRUE}
cor(df$Hours,df$Scores)
```
The above output confirms the high positive  correlation between the two variables.  

#### **Creation and Interpretation of the model** :  
Here, we have to predict the Score depending on the Hours of study. So clearly, *Scores* is the dependent variable and *Hours* is the independent variable.  

##### **Model**  
```{r echo=TRUE}
simple_model <- lm(Scores~Hours, data = df)
```
Now, we can get $\beta_0$ and $\beta_1$ created by the above model by:  
```{r echo=TRUE}
simple_model
```
Clearly,  
$\beta_0$ = 2.484  
$\beta_1$ = 9.776  

##### **Interpretation**  
```{r echo=TRUE}
summary(simple_model)
```
* The '***' at the end of the Hours in the above output shows that the independent variable has a significant impact on the dependent variable, Scores.
* *Multiple R-squared:  0.9529* means, nearly 95% of the variance in the values of Scores is explained by this simple model.
* *p-value: < 2.2e-16* is less than 0.05 and it shows that the model is of high significance.  

So, our model is :
$$y = 2.484 + 9.776*x$$ 

##### **Visual Representation of the Model**
```{r echo=TRUE}
ggplot(df , aes( x = Hours, y = Scores)) +
geom_point(color = 'red' , size = 3) +
labs (title = '\nSimple Linear Regression') +
geom_smooth(method='lm', formula= y~x)
```




#### **Prediction**
So, if a student studies for 9.25 hrs/day, then according the created model, the predicted Score of that student will be 92.912 as shown below :  
```{r echo=TRUE}
2.484 + 9.776*9.25
```